---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warnings = FALSE, 
  messages = FALSE, 
  prompt = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# genR

<!-- badges: start -->
<!-- badges: end -->

The goal of genR is to install generic functions to read and write files.  

Functions include selecting files to import, exporting tables to CSV files and reading and writing lists of objects to RDS files.

## Installation

You can install the development version of genR like so:

```{r, install, results = "hide", eval = FALSE}
# install.packages("remotes")
# remotes::install_github("pennydropper/genR")
```

## Example

This is a basic example which shows you how to use genR:

```{r example}
library(genR)
## basic example code
```

First, use a character vector to list the names of objects that you want to export to RDS files and import from RDS files.

Note that the objects can be of any type, including dataframes, tibbles, list objects etc.

```{r}

mtcars_cp <- mtcars
letter_cp <- letters

preserve_objs <- 
  c(
    "mtcars_cp",
    "letter_cp"
  )
```

Executing `write_dfs` will step through each name in the vector, confirm that an object with that name exists then export the object to an `.RDS` file in the specified directory.

Upon completion, `write_dfs` will confirm which objects were successfully exported to `.RFS` files.

```{r}
# write_dfs(preserve_objs, "~")
write_dfs(preserve_objs, "~")
```

Executing `retrieve_dfs` will step through each name listed in the vector, confirm whether an `.RDS` file with that name exists in the specified directory, then import that `.RDS` file and save it as an object with that name.

`retrieve_dfs` completes it's task by listing:  
-  Each file's modified date.  
-  The vector entries where an `.RDS` file was not found.

```{r}
retrieve_dfs(preserve_objs, "~")
```


